---
title: "Replication Report on Renshon (2014)"
author: "Sean Hughes"
output: html_document
---

## Abstract

I replicate and expand upon the work in “Physiological Arousal and Political Beliefs” (CITATION) using data and replication code from the Harvard Dataverse (CITATION). In this paper Renshon, Lee, and Tingley explore the effects of incidental emotions on political beliefs. Specifically, by showing that heightened physiological reactivity, measured by SCL, mediated the relationship between anxiety and anti-immigration attitude, they are able to provide evidence that emotions incidental to the decision process can have important effects on our political beliefs.

I replicate 2 figures and 1 table from the article (located in the Appendix below). I also test the results of the study using alternative modeling techniques.



```{r setup, include=FALSE}

# ************************
# Load Required Libraries
# ************************

knitr::opts_chunk$set(echo = TRUE)

# Replicates and Extension of code from "Physiological Arousal and Political Beliefs"
# I will be replicating Figures 2, 3 and Table 1.

library(tidyverse)
library(dplyr)
library(ggplot2)
library(mediation)
library(stargazer)
library(rstanarm)

```

```{r datasets, include=FALSE}

# **********************
# Load Required Datasets
# **********************

# Note that I will use stars to make the "title" of each section of
#   comments more readable

anxiety_data <-read.csv("./dataverse_files/anxiety.csv")
mturk_data <-read.csv("./dataverse_files/mTurk.csv")

```

```{r cleanData, echo=FALSE}

# *****************************************************
# Cleaning and Analyzing the Data to Improve Readiblity
# *****************************************************

# Start by renaming the variables. This is following the names that
#   they used in the stata file with some minor changes

clean_data <- anxiety_data %>%  
  rename("Anxiety_Condition" = anxcond3,
         "Immigration_DV" = immigration,
         "Conductivity_Mean" = SCDBradSelfReport1_mean,
         "Story_Condition" = storycond,
         "Anxiety_IV" = anxcond,
        "Ideology" = ideology,
        "Age" = age,
        "Race" = race,
        "Income" = income,
        "Education" = education) %>% 
  
  # Now we will clean up the values within the columns so that they make 
  #   intuitive sense when read

  
  
  # Analysis of "Anxiety_Condition"
  
  # Anxcond3 refers to the three different treatment conditions
  #   these are: RELAX, NEUTRAL, ANXIETY (labeled 0,1,2)
  # Note that there is one NA value here which I have removed
  
  filter(!is.na(Anxiety_Condition)) %>% 
  
  # In the stata code, table 1 has the clause if anxcond3 ~=0
  #   it also states that table 1 excludes the "relax" condition
  #   so we know that 0 is the relax condition
  # In the stata code for appendix H, we can see that model 1 is neutral
  #   condition and model 2 is anxiety condition. They use the values 1 
  #   and 2 from the anxcond3 column respectivly to make these, so we 
  #   also know these values

  mutate (Anxiety_Condition = case_when(
                                Anxiety_Condition == 0 ~ "Relax",
                                Anxiety_Condition == 1 ~ "Neutral",
                                TRUE ~ "Anxiety"
                                )) %>% 
  
  
  # Analysis of "Immigration_DV"
  
  # The immigration column, labeled immigration DV, presumably means 
  #   immigration dependant variable as this is measured during the survey
  #   after the experiment occurs (i.e. this is the outcome)
  # The min is 1, the max is 5, so we can assume that this refers to 
  #   the immigration preferences given by the 5 point scale in the survey
  # These preferences range from "strongly agree" to "strongly disagree"
  # In the appendix it states that "higher values represent more 
  #   anti-immigrant attitudes"
  # This is given as a dbl in the r code, which shows that it is a mix of the 
  #   answers to the 5 questions regarding immigration from the appendix.

  
  # Analysis of "Conductivity_Mean"

  # SCD refers to Skin Conductance. We know this because of its use in figure 3
  #   in the appendix. 
  # Skin conductance was measured during the immigration questionnaire.
  # There are 10 NA's here, which could suggest that some people did not want to
  #   be tested in this manner?
  # A higher skin conductance indicates more anxiety


  # Analysis of Story_Condition

  # The participants were primed with an immigration story frame before shown the
  #   video condition. 
  # This column only contains values 0 and 1.
  # It can be assumed by their ordering in the appendix / discussion in the text
  #   that Jose is condition 0 and Niko is condition 1 (the names of the two conditions)

  mutate(Story_Condition = case_when(
                                Story_Condition == 0 ~ "Jose",
                                TRUE ~ "Niko"
                                )) %>% 

  
  # Analysis of Anxiety_IV

  # This variable is described as an indicator variable for the treatment status
  #   Its values are exculsively 0 and 1, and its mean value is .295
  # We can see by comparing this to the Anxiety Condition column, that the value
  #    it 1 when the condition is Anxiety, and 0 otherwise
  # This makes intuitive sense why the mean value is near .3, as there are 3 conditions
  #   so it should be about a third of the total number.


  # I reached out to the authors of the paper and they were able to provide copies
  #   of the questionares for the pretreatment survey:

  # Analysis of Ideology Column

  # This variable is part of the pretreatment demographic survey. It includes things
  #   like party identification
  # Values taken from pretreatment survey:

  mutate(Ideology = case_when(
                        Ideology == 1 ~ "Extremely Liberal",
                        Ideology == 2 ~ "Liberal",
                        Ideology == 3 ~ "Slightly Liberal",
                        Ideology == 4 ~ "Moderate",
                        Ideology == 5 ~ "Slightly Conservative",
                        Ideology == 6 ~ "Conservative",
                        Ideology == 7 ~ "Extremely Conservative"
                        )) %>% 


  # Analysis of Race Column

  # This variable is part of the pretreatment demographic survey.
  # It contains values 1 through 7. There is one NA.
  # It doesn't seem like they give info regarding what the different categories
  #   indicate
  
  mutate(Race = case_when(
                      Race == 1 ~ "Caucasian",
                      Race == 2 ~ "African American",
                      Race == 3 ~ "Asian",
                      Race == 4 ~ "Hispanic",
                      Race == 5 ~ "Native American",
                      Race == 6 ~ "Pacific Islander",
                      Race == 7 ~ "Other"
                      )) %>% 

  # Analysis of Income Column
  
  # Income is also avaliable on the pretreatment survey
  
  mutate(Income = case_when(
                    Income == 1 ~ "$0-24,999",
                    Income == 2 ~ "$25,000-49,999",
                    Income == 3 ~ "$50,000-79,999",
                    Income == 4 ~ "$80,000-110,000",
                    Income == 5 ~ "$110,000 -150,000",
                    Income == 6 ~ "$150,000-200,000",
                    Income == 7 ~ "$200,000"
                    )) 

```

## Extension Analysis

I will further explore the studies findings regarding the Effects of Physiological Arousal on Immigration Preferences. Specifically, this means comparing the significance of treatment vs. the responses to the immigration questionare. We take these variables and run a series of models to verify the robustness of the results.

## Basic Linear Model

Using the main results table (Appendix Table 1) the authors claim that skin conductance reactivity is a significant predictor of immigration preference. Note that the authors of the paper choose to filter out data from the "RELAX" condition, citing that the results remain unchanged if included. We will include the RELAX condition and combine the 3 treatments into a binary variable with the following values:
- 1 if treatment condition is Anxiety
- 0 if treatment condition is Neutral or Relax
The authors claim that treatment is a significant predictor of SCL. They also claim that skin conductance reactivity is a significant predictor of immigration preference. While these claims together might appear to suggest that treatment condition was a significant predictor of the immigration DV, we can see below that it is not. 


```{r extension, echo=FALSE, results='asis'}

# ******************
# BASIC LINEAR MODEL
# ******************

# PUT THIS SOMNEWHERE:

#We will be examining the results via casual inference. The variable treatment has a value of 1 if the participant was part of the treatment group (receiving the ANXIETY condition in the pretreatment video) or a value if the participant was part of the non-treatment group (receiving the RELAX or NEUTRAL conditions in the pretreatment video). We see that the potential outcomes are equal to __ and __. This means that our estimated treatment effect is __.


# We will conduct a series of linear regressions to judge the treatment effect
# The left hand variable will be the outcome variable (immigration questionare)
# The right hand variable will always include treatment

# Basic linear model with outcome variable and treatment

# Filter data such that anxiety condition relax is not included

lm1_data <- clean_data %>%
  
  # Filter data so that no NA values are included
  
  filter(!is.na(Anxiety_Condition)) %>% 
  
  filter(!is.na(Anxiety_IV)) %>% 
  
  filter(!is.na(Immigration_DV)) %>% 
  
  filter(!is.na(Story_Condition))

# Linear Regression 1

lm1 <- lm(Conductivity_Mean ~ Anxiety_IV, 
   data = lm1_data)

# Linear Regression 2

lm2 <- lm(Immigration_DV ~ Anxiety_IV, 
   data = lm1_data)

# Linear Regression 2

lm3 <- lm(Immigration_DV ~ Conductivity_Mean, 
   data = lm1_data)

# Use stargazer to plot the output

stargazer(lm1, lm2, lm3,
          type="html",
          notes = "Model (1) shows the effect of the treatment (anxiety) on physiological reactivity while Model (2) shows the effects of physiological reactivity on immigration preferences, controlling for the story condition. Both models includes only Neutral and Anxiety conditions (Relax condition is excluded). Standard errors in brackets.",

          notes.align = "l",
          title="Table 1. Basic Linear Models",
          keep.stat=c("n", "rsq")
          )

```

## Linear Model With Interaction Items

#### Model 1

Note that gender was not included in the dataset, though it was included in the pretreatment survey.
```{r}

# ***********************************
# Linear Model With Interaction Items
# ***********************************

# I use indentation to help organize the different models' code

# Model 1: Look at Pretreatment Demographic Variables

  # Create a new dataset for model 1

  lm1_data2 <- lm1_data %>% 

  # Step 1: Create dummy variables

    # Ideology
  
    # We create a dummy variable for ideology such that any ideology
    # that is "past" moderate on their 1 - 7 scale is considered a 
    # conservative ideology. We thus make them have a value of 1 as 
    # being conservative, and all other ideologies (ranging from moderate
    # to very liberal) are given a value of 0

    mutate(Ideology_Dummy = case_when(
                Ideology %in% c("Conservative", 
                               "Slightly Conservative", 
                               "Extremely Conservative") ~ 1,
                TRUE ~ 0
    ))  %>% 

    # Income

    # According to https://fred.stlouisfed.org/series/MEHOINUSA646N, US Median
    #   Income was $53,657 in 2014 (The year this paper was published). We create
    #   our dummy variable such that values of income greater than the bracket including 
    #   this number are a 1, and income leves less than the bracket we includ here are a 0
  
    mutate(Income_Dummy = case_when(
                Income %in% c("$80,000-110,000", 
                               "$110,000 -150,000", 
                               "$150,000-200,000",
                               "$200,000") ~ 1,
                TRUE ~ 0
    ))  %>% 
  
    # Race
  
    mutate(Income_Dummy = case_when(
                Income %in% c("$80,000-110,000", 
                               "$110,000 -150,000", 
                               "$150,000-200,000",
                               "$200,000") ~ 1,
                TRUE ~ 0
    )) 

    # Gender

    # Education

lm1_data

# Linear Regression 1

lm1 <- lm(Conductivity_Mean ~ Anxiety_IV, 
   data = lm1_data)

# Linear Regression 2

lm2 <- lm(Immigration_DV ~ Anxiety_IV, 
   data = lm1_data)

# Linear Regression 2

lm3 <- lm(Immigration_DV ~ Conductivity_Mean, 
   data = lm1_data)

# Use stargazer to plot the output

stargazer(lm1, lm2, lm3,
          type="html",
          notes = "Model (1) shows the effect of the treatment (anxiety) on physiological reactivity while Model (2) shows the effects of physiological reactivity on immigration preferences, controlling for the story condition. Both models includes only Neutral and Anxiety conditions (Relax condition is excluded). Standard errors in brackets.",

          notes.align = "l",
          title="Table 1. Basic Linear Models",
          keep.stat=c("n", "rsq")
          )




```


## Appendix

### Figure 2: Skin Confuctivity Confidence Intervals

When calculating the mean points for the different treatments I receive different results than are demonstrated in the paper. However, these results still show the same trend as shown in the paper: that the anxiety video condition effectively causes the user to experience anxiety and that the relax condition causes the amount of anxiety to be reduced. These results assume that Skin Conductivity Reactivity is a reasonable gauge of anxiety as described in the paper.

```{r figure2, echo=FALSE}

# **************************************************************
# Recreating Figure 2: Skin Conductivity vs. Treatment Condition
# **************************************************************

# For this graph we need dots showing the mean of the values, and also
#   lines showing the 95% confidence interval for the values

# First, we will calculate the means of the treatment conditions and 
#   create the plot with just the points of the means on the graph

p1 <- clean_data %>% 
  
  # Filter out all lines where there is no conductivity data
  
  filter(!is.na(Conductivity_Mean)) %>% 
  
  # Group by the 3 different treatment conditions so that we
  #   can analyze differences between the treatments
  
  group_by(Anxiety_Condition) %>% 
  
  # Use the summarize function to gather the mean of the three
  #   different conditions
  
  summarize(mean_value = mean(Conductivity_Mean)) %>% 
  
  # Use fct_relevel to edit the ordering of the three columns
  
  mutate(Anxiety_Condition = fct_relevel(Anxiety_Condition, c("Relax", "Neutral", "Anxiety"))) %>% 
  
  # Use ggplot to output the point data for the graph
  
  ggplot(aes(x = Anxiety_Condition, y = mean_value))

# Next we will calculate the 95% confidence intervals


# I will create a function that on input a given condition and 
#   its skin conductivity values outputs the correct conductivity
#   intervals

conduct_intervals <- function(data, name) {

  # Inspiration for this section was taken from an R tutorial on
  #   Cyclismo: https://www.cyclismo.org/tutorial/R/confidence.html
  
  # Calulcate the nuber of data points
  
  relax_n <- data %>% nrow()
  
  # Calculate the mean of the data points
  
  relax_a <- mean(data$Conductivity_Mean)
  
  # Calculate the standard deviation of the data
  
  relax_s <- sd(data$Conductivity_Mean)
  
  # qt returns the value of the 95th percentile of a distribution, this function
  #    thus calculates the distance tht the 95th percentile will be from the mean
  
  error <- qt(0.95, df = relax_n - 1) * relax_s / sqrt(relax_n)
  
  # Uses the error to calculate the left bound and right bound
  
  left <- relax_a-error
  
  right <- relax_a+error
  
  # Create a data frame to store the outcomes
  
  test_frame <- setNames(data.frame(matrix(ncol = 3, nrow = 1)), c("condition", "left", "right"))
  
  # Append the sd data to the data frame
  
  test_frame$condition[1] = name
  test_frame$left[1] = left
  test_frame$right[1] = right
  
  # Output the data frame with the correct functions in it
  
  test_frame

}

# We use a series of filter commands to create the correct inputs
#   for our function
# These commands elimnate all NA values, filter for the correct condition,
#   and input the "name" paramater so that the function can correctly assign
#   values for ggplot

relax_intervals <- clean_data %>% 
  filter(Anxiety_Condition == "Relax") %>% 
  filter(!is.na(Conductivity_Mean)) %>% 
  conduct_intervals("Relax")

neutral_intervals <- clean_data %>% 
  filter(Anxiety_Condition == "Neutral") %>% 
  filter(!is.na(Conductivity_Mean)) %>% 
  conduct_intervals("Neutral")

anxiety_intervals <- clean_data %>% 
  filter(Anxiety_Condition == "Anxiety") %>% 
  filter(!is.na(Conductivity_Mean)) %>% 
  conduct_intervals("Anxiety")

# Use an rbind command to group the outputs together for ggpot

all_intervals <- rbind(rbind(relax_intervals, neutral_intervals), anxiety_intervals) %>% 
  
  # Use fct_relevel to edit the ordering of the three columns
  
  mutate(condition = fct_relevel(condition, c("Relax", "Neutral", "Anxiety"))) 
  

# use a geom_segment function to display the confidence intervals

p1 +  geom_segment(data = all_intervals,
               
               aes(x = condition, 
                   xend = condition, 
                   y = left, 
                   yend = right),
               size = 2,
               colour = "#FCD29F") +
  
  # Use geom_point to display the means

      geom_point(colour = "#FCAB64", size = 5) +
  
  # Add in labels for readibility
  
      labs(x = "Video Condition", 
           y = "Skin Conduction Reactivity",
           title = "Confidence Intervals of Video Condition vs. Skin Conduction Reactivity") +
  
  # Add in thee_bw for aesthetics
  
      theme_bw()

```


### Figure 3: Causual Mediation Plot

I was able to succesfully recreate all of figure 3.

```{r figure3, echo=FALSE}

# **************************************************************
# Recreating Figure 3: 
# **************************************************************

# I cleaned up their R code for this section to make it more legible

# Filter to remove the relaxed condition

data_norelax <- clean_data %>% 
  
  filter(Anxiety_Condition != "Relax")

# Outcome Model

y <- lm(Immigration_DV ~ Anxiety_IV + Conductivity_Mean + Story_Condition, data= data_norelax)

# Mediator Model

m<- lm(Conductivity_Mean ~ Anxiety_IV + Story_Condition, data= data_norelax)

# Mediation Analysis

m.out<-mediate(m,y, sims=500, treat="Anxiety_IV", mediator="Conductivity_Mean", dropobs=TRUE, boot=TRUE, conf.level=.90)

# Plot the Output

par(mar=c(5,6,4,1)+.1)
plot(m.out, labels=c("ACME\n(Physiological \nReactivity)", "Direct Effect \n(Anxiety)", "Total Effect"))
mtext("Figure 3: Causal mediation plot. Treatment is anxiety video manipulation (compared to 
neutral condition), Mediator is skin conductance reactivity when answering 
immigration questions, Outcome is composite variable of immigration preferences.
Horizontal lines represent 90% confidence intervals for estimates.",side=1,line=5,adj=0) 

```

### Table 1: Main Results

I was able to succesfully recreate all of table 1.

```{r table1, echo=FALSE, results="asis"}

# ********************************
# Recreating Table 1: Main Results
# ********************************

# Filter data such that anxiety condition relax is not included

lm1_data <- clean_data %>% 
  
  filter(Anxiety_Condition != "Relax") %>% 
  
  # Filter data so that no NA values are included
  
  filter(!is.na(Anxiety_Condition)) %>% 
  
  filter(!is.na(Anxiety_IV)) %>% 
  
  filter(!is.na(Immigration_DV)) %>% 
  
  filter(!is.na(Story_Condition))

# Linear Regression 1

lm1 <- lm(Conductivity_Mean ~ Anxiety_IV, 
   data = lm1_data)

# Linear Regression 2

lm2 <- lm(Immigration_DV ~ Anxiety_IV + Story_Condition + Conductivity_Mean, 
   data = lm1_data)

# Use stargazer to plot the output

stargazer(lm1, lm2, 
          type="html",
          notes = "Model (1) shows the effect of the treatment (anxiety) on physiological reactivity while Model (2) shows the effects of physiological reactivity on immigration preferences, controlling for the story condition. Both models includes only Neutral and Anxiety conditions (Relax condition is excluded). Standard errors in brackets.",
          covariate.labels = c("Anxiety Manipulation",
                               "Story Condition",
                               "SC Reactivity while answering questions",
                               "Constant"),
          notes.align = "l",
          title="Table 1. Main Results",
          keep.stat=c("n", "rsq")
          )
```


